### 2017-10-31 submission/manuscript.Rmd
change title
change hperlink

# The Importance of the Microbiota and Individual Community Members in Colorectal Cancer

@@

***Reproducible Methods:***
The code and analysis can be found here https://github.com/SchlossLab/Sze_CRCMetaAnalysis_XXXX_2016. Unless mentioned otherwise the accession number for the raw sequences for the studies used in this analysis can be found directly in the respective batch file, on the GitHub repository or in the original manuscript.

>>>>

# The Microbiota and Individual Community Members in Colorectal Cancer: Is There a Common Theme?

@@

***Reproducible Methods:***
The code and analysis can be found here https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017. Unless mentioned otherwise the accession number for the raw sequences for the studies used in this analysis can be found directly in the respective batch file, on the GitHub repository or in the original manuscript.
